\section{Main Functionalities}

The Recipe Sharing Platform is an online community designed to cater to culinary enthusiasts, providing them access to a diverse collection of recipes and fostering interaction among users. The platform offers functionalities tailored to accommodate various types of users, including Admins, Registered Users, and Regular Visitors, each with their own level of engagement and access privileges.

\subsection{Admin}

Administrators of the Recipe Sharing Platform play an important role in overseeing platform operations and ensuring user compliance with platform policies. They have access to a range of functionalities geared towards maintaining smooth functionality and enhancing user experience.

\textbf{User Management:}
\begin{itemize}
  \item Administrators possess the authority to manage user accounts, including the ability to delete accounts when necessary and update account details such as usernames, email addresses, and profile information. This ensures that the platform maintains a safe and secure environment for all users.
\end{itemize}

\textbf{Access to Main Functionalities:}
\begin{itemize}
  \item Admins enjoy access to all functionalities available to registered users, enabling them to interact with recipes, rate, comment, and manage their own recipe collections. This allows administrators to actively engage with the community and participate in culinary discussions.
\end{itemize}

\textbf{Modify Website Settings:}
\begin{itemize}
  \item They have the capability to adjust website settings, including homepage layout, theme customization, and general configurations, to optimize user experience. This flexibility empowers administrators to tailor the platform according to user preferences and trends in the culinary community.
\end{itemize}

\subsection{Registered User}
Registered users constitute the core community members of the Recipe Sharing Platform, actively engaging with recipes, sharing culinary creations, and interacting with fellow users. They benefit from a variety of features tailored to enhance their culinary journey on the platform. 

\textbf{User Registration and Login:}
\begin{itemize}
  \item Users can easily register for an account, providing necessary information such as username, email address, and password. Once registered, they gain access to personalized features and content upon logging in. This streamlined registration process encourages user participation and fosters a sense of belonging within the community.
\end{itemize}

\textbf{Modify Profile:}
\begin{itemize}
  \item Registered users have the flexibility to update their profile information, manage account settings, and personalize their profiles with profile pictures, ensuring a customized experience. This allows users to curate their online identity and showcase their culinary preferences and expertise.
\end{itemize}

\textbf{Recipe Management:}
\begin{itemize}
  \item Registered users can contribute to the platform by creating and uploading their own recipes, sharing their culinary expertise with the community. They can also interact with recipes by liking, rating, and commenting, fostering community engagement and feedback. This collaborative approach to recipe management encourages users to share their culinary creations and engage in meaningful discussions with other members.
\end{itemize}

\textbf{Recipe Interaction and Sharing:}
\begin{itemize}
  \item Users can interact with recipes by rating and commenting, facilitating dynamic exchanges of culinary insights and tips. Additionally, they can share their own recipes, enriching the platform's recipe database and promoting community interaction. This interactive platform feature encourages users to actively participate in the culinary community, share their cooking experiences, and learn from others.
\end{itemize}

\subsection{Regular Visitor}

Regular Visitors are users who access the Recipe Sharing Platform without registering for an account. While they have limited access compared to registered users, they can still explore the platform and browse through recipes.

\textbf{View Recipes:}
\begin{itemize}
  \item Regular Visitors can browse and view recipes available on the platform without the need to register or log in. They can explore recipes based on various criteria such as cuisine type, ingredients, or dietary restrictions. This allows casual users to discover new recipes and culinary inspirations without the commitment of creating an account.
\end{itemize}

\subsection{Main Areas}

\textbf{Public Area:}
\begin{itemize}
  \item The Public Area serves as the homepage/landing page of the platform, accessible to both unregistered users and registered users with basic privileges. Here, users can browse and search for recipes based on various criteria such as cuisine type, ingredients, or dietary restrictions. This central hub provides easy access to the platform's content and encourages users to explore the diverse range of recipes available.
\end{itemize}

\textbf{Registered User Area:}
\begin{itemize}
  \item Reserved for users with registered accounts, the Registered User Area offers additional functionalities beyond those available to unregistered users. Here, registered users can engage more deeply with the platform, including creating and sharing recipes, interacting with other users, and accessing personalized features. This dedicated space fosters a sense of community among registered users and encourages active participation in platform activities.

\end{itemize}

\textbf{Admin Area:}
\begin{itemize}
  \item The Admin Area provides administrators with a comprehensive overview of platform activities, including recipe management and user statistics. Admins can monitor recipe uploads, user engagement metrics, and platform performance to ensure smooth operation and user satisfaction. This administrative dashboard empowers administrators to make informed decisions and implement strategies to enhance the platform's functionality and user experience.
\end{itemize}


